---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Meteorological data

<!-- badges: start -->
<!-- badges: end -->

Source: [TuTiempo.net](https://en.tutiempo.net), daily data.

Station: 489400 (VLVT) | Latitude: 17.95 | Longitude: 102.56 | Altitude: 171

[cleaning pipeline](https://ecomore2.github.io/meteo/make_data.html)

[CSV](https://raw.githubusercontent.com/ecomore2/meteo/master/data/meteo.csv)

From R:

```{r}
if (! "readr" %in% rownames(installed.packages())) install.packages("readr")
pacs <- readr::read_csv("https://raw.githubusercontent.com/ecomore2/meteo/master/data/meteo.csv",
                        col_types = "Dddddidddddllll")
```

Dictionary:

* **day**: date of data colletion
* **ta**: average temperature (°C)
* **tx**: maximum temperature (°C)
* **tn**: minimum temperature (°C)
* **slp**: atmospheric pressure at sea level (hPa)
* **h**: average relative humidity (%)
* **pp**: total rainfall and / or snowmelt (mm)
* **vv**: average visibility (km)
* **v**: average wind speed (km / h)
* **vm**: maximum sustained wind speed (km / h)
* **vg**: maximum speed of wind (km / h)
* **ra**: boolean indicating whether there was rain or drizzle
* **sn**: boolean indicating whether it snowed
* **ts**: boolean indicating whether there were storm
* **fg**: boolean indicating whether there was flood
